# Abschließende Bemerkungen

Einige Hinweise für *`selbständige`* Textanalysen. 🤗

{{ \< include \_WM_Presentation.qmd \> }}

## Fontawesome

In the terminal use:  
quarto install quarto-ext/fontawesome

This extension folder has to be installed in every project.

After installation, use curly braces to include fa icons / or use html code (e.g. copy free icons from https://fontawesome.com , namely: https://fontawesome.com/start).

{{< fa envelope >}} - the code for an envelope

{{< fa brands facebook >}} - the code for brands like facebook

For icon-styling go to https://github.com/quarto-ext/fontawesome: 
{{< fa brands windows size= 4x >}}

On https://fontawesome.com/docs, there is information on how to change the color of the icons, e.g. in the Styling section, Basics.

<span style="font-size: 3em; color: Tomato;">
    <i class="fa-solid fa-camera"></i>
  </span>
  
Rotated icons:  

<div class="fa-3x">
<i class="fa-solid fa-snowboarding"></i>
<i class="fa-solid fa-snowboarding fa-rotate-90"></i>
<i class="fa-solid fa-snowboarding fa-rotate-180"></i>
<i class="fa-solid fa-snowboarding fa-rotate-270"></i>
<i class="fa-solid fa-snowboarding fa-flip-horizontal"></i>
<i class="fa-solid fa-snowboarding fa-flip-vertical"></i>
<i class="fa-solid fa-snowboarding fa-flip-both"></i>
</div>


Possible to include animated icons:  

<div class="fa-3x">
  <i class="fa-solid fa-basketball fa-bounce"></i>
  <i class="fa-solid fa-volleyball fa-bounce"></i>

  <!-- bounce animation with no "squish" -->
  <i class="fa-solid fa-frog fa-bounce" style=" --fa-bounce-start-scale-x: 1; --fa-bounce-start-scale-y: 1; --fa-bounce-jump-scale-x: 1; --fa-bounce-jump-scale-y: 1; --fa-bounce-land-scale-x: 1; --fa-bounce-land-scale-y: 1; " ></i>

  <!-- bounce animation with no "squish" or "rebound" -->
  <i class="fa-solid fa-envelope fa-bounce" style=" --fa-bounce-start-scale-x: 1; --fa-bounce-start-scale-y: 1; --fa-bounce-jump-scale-x: 1; --fa-bounce-jump-scale-y: 1; --fa-bounce-land-scale-x: 1; --fa-bounce-land-scale-y: 1; --fa-bounce-rebound: 0;" ></i>
</div>



## Callout Types

::: {.callout-note}
Note that there are five types of callouts, including: `note`, `warning`, `important`, `tip`, and `caution`.
:::

::: callout-tip
## Tip With Caption / Tipp mit Titel

This is an example of a callout with a caption.
:::

::: callout-important
Das ist wichtig.
:::

::: callout-warning
Warning
:::

::: {.callout-caution collapse="true"}
## Expand To Learn About Collapse

This is an example of a 'folded' caution callout that can be expanded by the user. You can use `collapse="true"` to collapse it by default or `collapse="false"` to make a collapsible callout that is expanded by default.
:::

## DiagrammeR mermaid

```{r}
library(DiagrammeR)
# https://rich-iannone.github.io/DiagrammeR/mermaid.html

mermaid("
graph LR
  A-->B
  A-->C
  C-->E
  B-->D
  C-->D
  D-->F
  E-->F
")
```

```{r}
mermaid("graph LR; A-->B; A-->C; C-->E; B-->D; C-->D; D-->F; E-->F")
```

```{r}
mermaid("graph TB; A-->B; A-->C; C-->E; B-->D; C-->D; D-->F; E-->F")
```

```{r}
mermaid("
graph LR
  A[node text]
")

mermaid("
graph LR
  A(node text)
")

mermaid("
graph LR
  A((node text))
")

mermaid("
graph LR
  A{node text}
")

mermaid("
graph LR
  A>node text]
")

mermaid("
graph LR
A(Rounded)-->B[Rectangular]
B-->C{A Rhombus}
C-->D[Rectangle One]
C-->E[Rectangle Two]
")
```

```{r}
mermaid("
sequenceDiagram
  customer->>ticket seller: ask ticket
  ticket seller->>database: seats
  alt tickets available
    database->>ticket seller: ok
    ticket seller->>customer: confirm
    customer->>ticket seller: ok
    ticket seller->>database: book a seat
    ticket seller->>printer: print ticket
  else sold out
    database->>ticket seller: none left
    ticket seller->>customer: sorry
  end
")
```
